---
title: "Mini-Project 2"
author: "Lisa Chen and Yejin Hwang"
date: "October 31, 2017"
output: html_document
---

```{r, include = FALSE}
## Loading the data
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```

```{r, include = FALSE}
library(dplyr)
library(tidyverse)
library(ggplot2)
```

```{r, eval=FALSE}
# selected columns for smaller dataframes and saved prior to wrangling
candidate_info <- candidates %>%
  select(cand_id, cand_name, cand_party_affiliation, cand_election_yr, cand_office)
save(candidate_info,file="candidate_info.rda")
glimpse(candidate_info)

committee_info <- committees %>%
  select(cmte_id, org_type, cand_id)
save(committee_info,file="committee_info.rda")
glimpse(committee_info)

contribution_info <- contributions %>%
  select(cmte_id,transaction_amt,cand_id)
save(contribution_info,file="contribution_info.rda")
glimpse(contribution_info)
```
####Data Wrangling
```{r}
# Load created data ------------------------------------------------
load("candidate_info.rda")
load("committee_info.rda")
load("contribution_info.rda")

# Use inner_join to combine datasets -------------------------------
join_two <- contribution_info %>%
  inner_join(candidate_info, by = c("cand_id"="cand_id"))

joined_three <- join_two %>%
  inner_join(committee_info, by = c("cmte_id"="cmte_id"))

# Filter data for only Democratic, Republican, and for the years 2009-2013
joined_three <- joined_three %>%
  filter(cand_party_affiliation == "DEM" | cand_party_affiliation == "REP") %>%
  filter(cand_election_yr >=2009 & cand_election_yr <=2013)
```
Because `inner_join` was done specifically to `cand_id` and not to `other_id` (FEC ID of the recipient committee or the supported or opposed candidate ID), the data is limited to candidates receiving money from the filing committee directly.
```{r}
#sum up individual transactions --------------------------------------
joined_threes <- joined_three %>%
  group_by(cand_office, org_type, cand_party_affiliation) %>%
  summarize(trans_amt = sum(transaction_amt)) %>%
  mutate(trans_amt = trans_amt/10^6)
#divide joined_three to two data sets --------------------------------
#1 - with org_types
w_org <- joined_threes %>%
  filter(org_type != "") 
#2 - observations that don't have org_types
w_o_org <- joined_threes %>%
  filter(org_type == "")
```
```{r}
#rename office labels for facet_wrap ---------------------------------
#(to be used when plotting)
var_to_string <- as_labeller(c(
  'H' = "House",
  'S'="Senate",
  "P" = "Presidential"
))
```
####Usage of function()
```{r}
#function for plotting basic aesthetics of data
FilL <- c("#232066", "#E91D0E")
by_office_bar <- function(dtfrm){
  ggplot(data = dtfrm, aes(x = org_type, y=trans_amt, fill = cand_party_affiliation)) +
    geom_bar(width=0.8, position = position_dodge(width=0.6), stat="identity") +
    scale_fill_manual(values=FilL, name = "Candidate Party\n   Affiliation") +
    facet_wrap(~cand_office,labeller=var_to_string) +
    labs(x="Organization Type",y="Transaction Amount\n(in Millions)") +
    scale_y_continuous(labels = scales::dollar_format())
}
```
####Tailoring the Graphs:
##Graph A
```{r,fig.height=9, fig.width=14}
plot_A <- by_office_bar(w_org) +
  scale_x_discrete(labels = c("Corp.","Labor\n  org.","Membership\n   org.","Trade \n assoc.","Co-op","Corp. w/o \n capital stock")) +
    theme(strip.text = element_text(face="bold", size = 15),
          axis.text=element_text(size=8),
          legend.text = element_text(face="bold",size = 10))
plot_A
```





This graph shows
Yet, there was a significant amount of other transactions 
**explaining in a single coherent sentence what we can learn from these data**

##Graph B
```{r,fig.height=5, fig.width=5}
plot_B <- by_office_bar(w_o_org) +
  theme(axis.ticks.x =element_blank()) +
    theme(strip.text = element_text(face="bold", size = 7),
          axis.text=element_text(size=6),
          legend.text = element_text(face="bold",size = 7))
plot_B

```
This graph shows
**blog post text provides context or background useful in interpreting the graphic**



